A sample workflow

### 2025-05-02 analyses/lpiworkflow.qmd
add a plot with some replications

## Step 1: Research question

@@

## Step 2: Model building

@@

## Step 3: Model evaluation

@@

### Stepping backward...

@@

### Simulating data

@@

```{r sim data}

@@

### Fit and check model on simulated data!

@@

#### Checking model fitted on simulated data

@@

## Step 4: Fit model to empirical data

@@

```{r units}
#| eval: true
#| layout-nrow: 2

@@

```{r fitdata}
#| eval: true

@@

lpi_subset_rsh <- lpi_subset_rsh[lpi_subset_rsh$value != 0,] # We now also find we have counts of 0, which is tricky for our approach (as we cannot evaluate log(0)), we would also flag this to return. As we iteratively improve the model, we would need to consider what processes generate these zeroes, and include them in our model.

@@

## Step 5: Retrodictive and related checks

@@

Here we start by visually comparing the posterior predictive distribution (red line) to observed data (black dashed line):
```{r}
#| fig-height: 5
#| fig-width: 5
#| echo: false

@@

@@

## Inference

@@

## Feedbacks

@@

## The full process

>>>>

# Step 1: Research question

@@

# Step 2: Model building

@@

# Step 3: Model evaluation

@@

## Stepping backward...

@@

## Simulating data

@@

```{r sim data}
#| fig-height: 4
#| fig-width: 7

@@

## Fit and check model on simulated data!

@@

@@

# Step 4: Fit model to empirical data

@@

```{r units}
#| eval: true
#| layout-nrow: 2
#| fig-height: 4
#| fig-width: 7

@@

```{r fitdata}
#| eval: true
#| fig-height: 4
#| fig-width: 7

@@

# We now also find we have counts of 0, which is tricky for our approach 
#(as we cannot evaluate log(0)), we would also flag this to return. 
# As we iteratively improve the model, we would need to consider what 
# processes generate these zeroes, and include them in our model.
lpi_subset_rsh <- lpi_subset_rsh[lpi_subset_rsh$value != 0,]

@@

# Step 5: Retrodictive and related checks

@@

Here we start by visually comparing the posterior predictive distribution (red line) to observed data (black dashed line):
```{r}
#| fig-height: 3
#| fig-width: 3
#| echo: false

@@

We can also look at some posterior replications separately:

```{r}
#| fig-height: 5
#| fig-width: 5
#| echo: false

n <- sample(1:4000, 9)
retrodictions <- (extract(fit, pars = names))
retrodictions_sub <- sapply(names, function(x){retrodictions[[x]][n]})

retrodictions_sub_df <- data.frame(ret = as.numeric(t(retrodictions_sub)), chain = rep(n, each = data$N))

ggplot() +
  facet_wrap(~ chain) +
  geom_density(data = data.frame(obs = log(data$y)), aes(x = obs), alpha = 0.5, linetype = 'dashed') +
  geom_density(data = retrodictions_sub_df, aes(x = ret), alpha = 0.5, col = 'darkred') +
  theme_bw() +
  labs(y = 'Density', x = 'Counts (log-scale)') +
  theme(strip.text.x.top = element_blank())

@@

# Inference

@@

# Feedbacks

@@

# The full process
